No Dogs On The Couch$_{Base}$

### 2012-11-20 Assignment6/paper/paper.tex

>>>>

\section{Workloads}
The following workloads were applied to the both the MySQL and Couchbase clusers.
\subsection{Assigning a Task}
TODO
\subsection{Profiling}
TODO
\subsection{Read and Writing Performance}
TODO
\subsection{Publishing}
TODO
\subsection{Adding and Removing Group Membership}
Adding or removing users to a group is a task common for classroom situations. In MySQL, this operation requires a join between three tables: Groups, Users, and GroupMembership. In Couchbase, this requires retrieving the key for the desired group and removing the user from the members field.
